---
title: "Composite Baro Data Generation Report"
author: "Nicholas Manna"
date: "`r lubridate::now()`" 
output: html_document
#initialize params. the markdown document will not knit with these defaults; proper params must be passed through rmarkdown::render
params:
  smp_id: 1-1-1
  start_date: 1/1/2019
  end_date: 1/31/2019
  data_interval: "5 mins"
  neighbors: a
  countNAs: b
  p: p
  csv_name: csv
  map: map
  baro_latest_dtime: a
  baro_latest_valid: b
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Create a date format to be used throughout document
sf <- lubridate::stamp("1/30/1999")
```

## `r params$smp_id`

On `r sf(lubridate::today())`, composite baro data was requested for SMP `r params$smp_id` from `r sf(params$start_date)` to `r sf(params$end_date)` at an interval of `r params$data_interval`. Output baro data is a result of a interpolation based on distance from the target baro. A minimum of four neighbors are needed to interpolate. Table 1 shows how many times each amount of baros were available for interpolation; for example, `r params$neighbors[1,1]` baro(s) were available at `r params$neighbors[1,2]` timesteps. If NA, and there are no interpolated data in Figure 1, then the requested smp has a baro on-site. 

Within the request interval, the latest date with baro data is `r params$baro_latest_dtime`. The latest date with four or more neighbors is `r params$baro_latest_valid`. 

The output file is below:  
`r params$csv_name`

<!-- This text is included if the data interval is 5 minutes -->
`r if(data_interval == "5 mins"){paste("Data for baro sensors that collected at 15 minute intervals had to be adjusted to be useful for 5 minute intervals. Gaps were filled by Last Object Carried Foward (LOCF). Table 2 shows how often that occured for each baro location.")}`


```{r tables, message=FALSE, echo = FALSE}
#Create a table listing neighbors and counts
  params$neighbors %>% 
    knitr::kable(caption = "Table 1: Frequency of Neighboring Baro Sensor Availability", format = "html") %>% 
    kableExtra::kable_styling(full_width = F, bootstrap_options = c("striped", "hover"), position = "float_left")

#Create a table listing LOCFs
if(data_interval == "5 mins"){
      params$countNAs %>% 
      knitr::kable(caption = "Table 2: Number of NAs that were replaced by Last Object Carried Forward (LOCF)", format = "html") %>% 
      kableExtra::kable_styling(full_width = F, bootstrap_options = c("striped", "hover"))
}

#show raster plot
params$p


```

`r kableExtra::text_spec("Figure 1: Baro Raster Plot", color = "grey")`

`r params$map`

`r kableExtra::text_spec("Figure 2: Baro Map with Target SMP", color = "grey")`
