---
title: "Composite Baro Data Generation Report"
author: "Nicholas Manna"
date: "`r lubridate::now()`" 
output: html_document
params:
  smp_id: 1-1-1
  start_date: 1/1/2019
  end_date: 1/31/2019
  data_interval: "5 mins"
  neighbors: a
  countNAs: b
  p: p
  
  
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sf <- stamp("1/30/1999")
```

## `r params$smp_id`

On `r sf(lubridate::today())`, composite baro data was requested for SMP `r params$smp_id` from `r sf(params$start_date)` to `r sf(params$end_date)` at an interval of `r params$data_interval`. Table 1 shows how many times each amount of baros were available for interpolation; for example, only `r params$neighbors[1,1]` baro was available at `r params$neighbors[1,2]` timesteps. 

`r if(data_interval == "5 mins"){paste("Data for baro sensors that collected at 15 minute intervals had to be adjusted to be useful for 5 minute intervals. Gaps were filled by Last Object Carried Foward (LOCF). Table 2 shows how often that occured for each baro location.")}`


```{r tables, echo = FALSE}
  params$neighbors %>% 
    knitr::kable(caption = "Table 1: Frequency of Neighboring Baro Sensor Availability") %>% 
    kableExtra::kable_styling(full_width = F, bootstrap_options = c("striped", "hover"), position = "float_left")

if(data_interval == "5 mins"){
      params$countNAs %>% 
      knitr::kable(caption = "Table 2: Number of NAs that were replaced by Last Object Carried Forward (LOCF)") %>% 
      kableExtra::kable_styling(full_width = F, 
                                bootstrap_options = c("striped", "hover"))
}

params$p

#ggsave("~/Reports/recentchart.png", plot = params$p, width = 8, height = 6, dpi = 300)

```



`r kableExtra::text_spec("Figure 1: Baro Raster Plot", color = "grey")`


